\section{Appendice} \label{sec:app}

\subsection{Tool utilizzati} \label{subsec:tool}

\begin{itemize}
	\item \LaTeX\ e l'editor TeXMaker : per redigere e strutturare questo documento
	\item Pencil : per la creazione dei mockups
	\item Draw IO: per la creazione dei grafici
	\item Gimp: per la creazione di mascotte e icone
\end{itemize}

\subsection{Acronimi} \label{acr}
Di seguito la lista degli acronimi utilizzati all'interno del documento:
\begin{acronym}[NDD] 
\acro{ndd}[NDD]{NeuroDevelopmental Disorder}
\acro{asd}[ASD]{Autistic Spectrum Disorders}
\acro{adhd}[ADHD]{Attention Deficit Hyperactivity Disorder}
\acro{gea}[GEA]{Gioco Educazione Alimentare}
\acro{vr}[VR]{Virtual Reality}
\acro{usb}[USB]{Universal Serial Bus}
\acro{hdmi}[HDMI]{High-Definition Multimedia Interface}
\acro{pc}[PC]{Personal Computer}
\acro{html}[HTML]{HyperText Markup Language}
\acro{css}[CSS]{Cascading Style Sheets}
\acro{php}[PHP]{Hypertext Preprocessor}
\end{acronym}

\clearpage

\subsection{Bibliografia} \label{subsec:biblio}
\renewcommand\refname{}
\begin{thebibliography}{100}
\bibitem{rif1} EPA, "United States Environmental Protection Agency". America's Children and the Environment | Third Edition, Updated October 2015. 
\url{https://www.epa.gov/sites/production/files/2015-10/documents/ace3_neurodevelopmental.pdf}
\bibitem{rif2} American Psychiatric Association, 2013. Diagnostic and statistical manual of mental disorders (DSM-5®). American Psychiatric Pub. 
\bibitem{rif3} Thomas D. Parsons, Giuseppe Riva, Sarah Parsons, Fabrizia Mantovani, Nigel Newbutt, Lin Lin, Eva Venturini, Trevor Hall. "Virtual Reality in Pediatric Psychology"
\url{http://pediatrics.aappublications.org/content/pediatrics/140/Supplement_2/S86.full.pdf}
\bibitem{rif4} Michelle Wang, Denise Reid. "Virtual Reality in Pediatric Neurorehabilitation:Attention Deficit Hyperactivity Disorder, Autism and Cerebral Palsy"
\url{https://www.karger.com/Article/Pdf/320847} 
\bibitem{rif5} "Effectiveness of virtual reality using Wii gaming technology in children with Down syndrome", Research in Developmental Disabilities Volume 32, Issue 1, January–February 2011, Pages 312-321
\bibitem{rif6} Yufang Cheng, PhD, Cheng-Li Huang, MA,Chung-Sung Yang, PhD. 2015. Using a 3D ImmersiveVirtual Environment System to Enhance SocialUnderstanding and Social Skills for Children WithAutism Spectrum Disorders. Focus on Autism andOther Developmental Disabilities, 30(4), 222–236.
\url{https://doi.org/10.1177/1088357615583473}
\bibitem{rif7}Franca Garzotto, Mirko Gelsomini, and DanieleOcchiuto. 2016 (Conference Paper). Wildcard: AWearable Virtual Reality Storytelling Tool for Children with Intellectual Developmental Disability AnnualInternational Conference of the IEEE Engineering inMedicine and Biology Society (EMBC’16)
\bibitem{rif8}"The evaluation of food pyramid games, a bilingual computer nutrition education program
for Latino youth", Journal of Family and Consumer Sciences Education, Vol. 22, No. 1, Spring/Summer 2004. Jennifer Anderson, Elena Serrano.
\url{https://www.researchgate.net/publication/253268811}
\bibitem{rif9} Google Cardboard. 
\url{https://vr.google.com/cardboard/}
\bibitem{rif10} Google Chromecast.
\url{https://chromecast.com}
\bibitem{rif11}Strickland, D., Marcus, L., Hogan, K., Mesibov, G., and McAllister, D. (1995). "Using virtual reality as a learning aid for autistic children". Proceedings of the Autisme France 3rd International Conference on Computers and Autism.
\bibitem{rif12}Dorothy Strickland. "A Virtual Reality Application with Autistic Children".
\bibitem{rif13}"Wildcard"
\url{www.wildcard.i3lab.me}
\bibitem{rif14}"Xoom"
\url{https://vima360.wordpress.com/}
\bibitem{rif15} HTC Vive.
\url{https://www.vive.com/us/product/vive-virtual-reality-system/}
\bibitem{rif16} Expo Milano 2015
\url{http://www.expo2015.org/}
\bibitem{rif17} "Nutrikid". Nestlé.
\url{https://www.buonalavita.it/nutrikid}
\bibitem{rif18} Nutrition Foundation of Italy.
\url{http://www.nutrition-foundation.it/homepage.aspx}
\bibitem{rif19} Food Education Italy.
\url{http://www.foodedu.it/it}

\end{thebibliography}